---
title: "HW5_gc2942"
name: "Guiqi Cai"
output: github_document
---

```{r setup,include=FALSE}
library(tidyverse)
library(viridis)
library(purrr)
knitr::opts_chunk$set(
  fig.width =6,
  fig.asp =0.6,
  out.width = "90%"
) 

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```


## Problem 1
```{r}
homicide_df = read.csv("./homicide-data.csv",na=c("","Unknown")) %>% 
  mutate(city_state = str_c(city,state),
  resolution =  case_when(disposition == "Closed without arrest"~"unsolved",
            disposition =="Open/No arrest"~"unsolved",
            disposition =="Closed by arrest"~"solved")) %>% 
  relocate(city_state) %>% 
  filter(city_state!= "TulsaAL")

```


```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
  baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n())

baltimore_test = 
  prop.test(
  x = baltimore_summary %>% pull(unsolved),
  n = baltimore_summary %>% pull(n))


baltimore_test %>% 
  broom::tidy()
```


```{r}
prop_test_function = function(city_df){
    city_summary = city_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n())
  city_test = 
  prop.test(
  x = city_summary %>% pull(unsolved),
  n = city_summary %>% pull(n))
  
  return(city_test)
}


prop_test_function(baltimore_df)

homicide_df %>% 
  filter(city_state=="AlbuquerqueNM") %>% 
  prop_test_function()
```

Now, let's iterate across all cities.
```{r}
results_df=homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(test_results = map(data,prop_test_function),
         tidy_results = map(test_results, broom::tidy)) %>% 
  select(city_state,tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state,estimate,starts_with("conf"))
                        
```

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x= city_state,y=estimate))+
  geom_point()+
  geom_errorbar(aes(ymin=conf.low,ymax=conf.high))+
  theme(axis.text.x = element_text(angle=90,vjust=0.5,hjust=1))
```
Alternative way..
```{r}
homicide_df %>% 
  group_by(city_state) %>% 
  summarize(unsolved = sum (resolution =="unsolved"),
            n=n()) %>% 
  mutate(
    test_results = map2(unsolved,n,prop.test),
    tidy_results = map(test_results, broom::tidy)) %>% 
  select(city_state,tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state,estimate,starts_with("conf"))
```


## Problem 2
Create a dataframe, import data by iterating over file names and read in data for each subject.
```{r,warning=FALSE}

file_df = 
  tibble(
    file =list.files("./data") ,
    vec_file = str_c("./data/",file)) %>% 
  mutate(group = map(vec_file, read.csv)) %>% 
  unnest()

```
Tidy the result-- manipulate file names to include control arm and subject ID.
```{r}
tidy_df=file_df %>% 
  select(-vec_file) %>% 
  pivot_longer(week_1:week_8,
               names_to = "week",
               values_to = "observation") %>% 
 separate(file,c("arm","subject_id"),"_") %>% 
 mutate(arm = case_when(arm == "con"~"Control Arm",
                        arm == "exp"~"Experiment Arm"),
         subject_id=str_replace(subject_id,".csv",""),
         week = as.integer(str_replace(week,"week_","")),
         arm =as.factor(arm))
      
```

Make a spaghetti plot showing observations on each subject over time

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = observation, color = subject_id)) + 
  geom_point() + 
  geom_line()+
  facet_grid(.~arm)+
  labs(title = "",
       x="week",
       y="observation",
       caption ="Data from the a longitudinal study")
```
The observation value in the experiment arm is larger than the value in the control arm.


## Problem 3
```{r}
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

I fill in missing values with the mean of non-missing values for numeric variables, and fill in missing values with "virginica" for character variables.

```{r}
fill_in_missing = function(x){
  if (is.numeric(x)){
    x=replace(x,is.na(x),mean(x,na.rm=TRUE))
  } 
  if (is.character(x)){
     x=replace(x,is.na(x), "virginica") 
  }
  return(x)
}
```


```{r}
output = map_df(iris_with_missing,fill_in_missing)
```



